% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{geometry}
\geometry{top=1.0cm, bottom=0.5cm}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number
\name{Yuju Shen}

\basicInfo{
  \email{denny.syj@hotmail.com} \textperiodcentered\
  \phone{(+86)15861812223} \textperiodcentered\
  \homepage{http://moon.nju.edu.cn/people/yjshen}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Nanjing University (NJU)}, Jiangsu, China}{Sep. 2016 -- Present}
\textit{M. Sc Student} in Dept. of Computer Science and Technology (CS), expected Jun. 2019
\datedsubsection{\textbf{Nanjing University (NJU)}, Jiangsu, China}{Sep. 2012 -- Jun. 2016}
\textit{B. Sc Degree} in Dept. of Computer Science and Technology (CS)

\section{\faUsers\ Internship}
\datedsubsection{\textbf{Tencent Inc.} Shenzhen, China}{Jun. 2018 -- Aug. 2018}
\role{Summer Intern, TEG}{C++/Python}
\begin{itemize}
  \item Testing environment building, unit testing, and stress testing of PCDN client (C++/Python)
  \item Writing a batch upgrade script for PCDN client (Python)
  \item Front-end development and testing of BitCoin automated trading system (Intern Project/Flask)
\end{itemize}

\section{\faSearch\ Projects}
\datedsubsection{\textbf{ReScue}}{Jun. 2017 -- Apr. 2018}
\role{Research Interest}{ASE'18, CCF-A, First Author, Distinguished Paper Award~\cite{shen2018rescue}}
A tool for the detection of regexes' DoS vulnerabilities. \\
Open source on GitHub: https://github.com/2bdenny/ReScue
\begin{itemize}
  \item Writing scripts to extract regexes from GitHub projects which implemented in different PLs
  \item Implementing ReScue based on genetic algorithm (with many optimizations)
  \item Implementing a visual tool that simulates regex's matching
\end{itemize}

\datedsubsection{\textbf{BungoHelper}}{Apr. 2017}
\role{For Fun}{JavaScript}
A chrome extension for web game, Bunka and Alchemist. \\
Open source on GitHub: https://github.com/2bdenny/Bungo\_Helper
\begin{itemize}
  \item Hijacking the response from server, extracting its hidden message and presenting it on devtool tab
\end{itemize}

\datedsubsection{\textbf{MR.Hunter}}{Nov. 2015 -- Nov. 2016}
\role{Research Interest}{Python, Web}
A demo of metamorphic testing (A test method for testing non-oracle programs).
\begin{itemize}
  \item Building an online-judge system for metamorphic testing code's submitting and automated varification
  \item Implementing user management, ranking, and duplicate code detection
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java > Python == C/C++
  \item Platform: Linux
  \item English: CET-6
\end{itemize}

%% Reference
%\newpage
\bibliographystyle{IEEEtran}
\bibliography{mycite}
\end{document}
